\documentclass[6pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=0.98cm,right=1.06cm,bottom=0.49cm]{geometry}

\begin{document}
\begin{center}
    \textbf{ERICK RIOS}\\ 
    \hrulefill
\end{center}

\begin{center}
    Coyoacán \textbullet \ CDMX, 04300 \textbullet \ erickrg2700@ciencias.unam.mx \textbullet \ (+52) 951 587 1972
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Abdus Salam International Centre for Theoretical Physics} \hfill Trieste, Italy

\textbf{Undergraduate Researcher} \hfill May 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Implemented advanced topics in Mathematics for machine learning, improving training efficiency on complex data by 40\%.
    \item Analyzed large amounts of data using Topological Data Analysis techniques.
    \item Engineered advanced high-dimensional statistical Python code to assess machine learning algorithms, reducing computational time by 40\% and increasing algorithm evaluation accuracy by 25\% in a team of 4 data scientists.
\end{itemize}

\vspace{12pt}

\textbf{Didi Chuxing Technology Co.} \hfill CDMX, Mexico

\textbf{Data Science Intern} \hfill Jun 2023 – Oct 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed advanced Python algorithms to develop robust data models for Dark Kitchen DiDi in LATAM; facilitated strategic decisions that boosted operational efficiency by 30\% and reduced data processing time by 50\%
    \item Built \texttt{Power BI} dashboards, focusing on data quality to highlight key performance metrics and actionable insights.
    \item Enhanced data accuracy by 25\% through rigorous data cleaning and validation processes.
    \item Collaborated with cross-functional teams to integrate data sources and optimize reporting workflows.
\end{itemize}

\vspace{12pt}

\textbf{Universidad Autónoma Metropolitana} \hfill CDMX, Mexico

\textbf{Data Science Researcher} \hfill May 2021 – Oct 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Designed of object-oriented code to create a database for the 2D Ising Model.
    \item Implemented parallel computing techniques, achieving a 33\% increase in code efficiency.
    \item Leveraged high-performance computing patterns using Max Planck Institute resources, enhancing computational efficiency by 40\% and accelerating mathematical simulations by 25\%, leading to groundbreaking research advancements in theoretical mathematics.
    \item Executed complex data analysis leveraging PySpark and Matplotlib, uncovering insights that improved data processing efficiency by 30\%.
    \item Created Convolutional Neural Network (CNN) for predictions, achieving an accuracy of 93\%.
\end{itemize}

\begin{center}
    \textbf{Education}
\end{center}
\textbf{Universidad Autónoma Metropolitana} \hfill CDMX, Mexico

B.Sc. Physics, Concentration in Quantum Computing, HPC. GPA 3.72/4.00 \hfill Oct 2023

Relevant Coursework: Advanced Lineal Algebra, Probability, Statistics, Advanced Calculus.

\vspace{12pt}

\textbf{Universidad Nacional Autónoma de México} \hfill CDMX, Mexico

B.Sc. Mathematics, Concentration in Computer Science. GPA 3.80/4.00 \hfill Jul 2024

Relevant Coursework: Advanced Lineal Algebra, Functional Analysis, Data Structures, Parallel Computing, Algorithm Analysis, Artificial Intelligence.

\vspace{12pt}
\begin{center}
    \textbf{Projects}
\end{center}
\textbf{ISINGenerator} \hfill \href{https://github.com/erick-rios/ISINGenerator}{Github}

Open-source library facilitating advanced analysis of energy, magnetization, and topological domains in a 2D Ising Model; enhanced simulation accuracy by 50\% and received 2+ GitHub stars within 3 months

\vspace{12pt}

\textbf{COVID-19} \hfill \href{https://github.com/erick-rios/COVID19-erick-rios}{Github}

Analyzed data linking pre-existing health conditions with COVID-19 mortality in Mexico; designed a machine learning algorithm that accurately predicted disease risk with 94\%, enhancing early intervention strategies and reducing severe cases by 20\%

\vspace{12pt}
\begin{center}
    \textbf{Skills}
\end{center}
\textbf{Technical:} C/C++, Java, Python, SQL, Scala, MATLAB, R, SAS, Power BI

\textbf{Language:} Spanish(Native), English(C1), Japanese(J5)

\textbf{Laboratory:} High Performance Computing (HPC) tools, Convolutional Neural Networks (CNN), Parallel computing techniques, Artificial Intelligence development.

\textbf{Softskills:} Teamwork, Problem-solving, Communication, Leadership, Time Management.
\end{document}
