\documentclass[6pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=0.98cm,right=1.06cm,bottom=0.49cm]{geometry}

\begin{document}
\begin{center}
    \textbf{ERICK JESUS RIOS GONZALEZ}\\ 
    \hrulefill
\end{center}

\begin{center}
    Coyoacán \textbullet \ CDMX, 04300 \textbullet \ erickjesusriosgonzalez@gmail.com \textbullet \  951 587 1972
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Faculty of Sciences, UNAM} \hfill CDMX, Mexico

\textbf{Teaching Assistant} \hfill Aug 2024 - Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Automated grade analysis and reporting with \texttt{Python}, reducing administrative workload by 30\%.
    \item Built \texttt{PowerBI} dashboards to track student performance, enabling real-time data-driven interventions.
    \item Analyzed academic trends for 8+ students, optimizing support strategies to improve learning outcomes.
\end{itemize}
\vspace{5pt}
\textbf{International Centre for Theoretical Physics } \hfill São Paulo, Brazil 

\textbf{(South America Institute for Fundamental Research)}

\textbf{Undergraduate Researcher} \hfill Oct 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Implemented quantum algorithms with Qiskit, improving data clustering efficiency by 40\%.
    \item Designed quantum computing models to discover patterns, boosting analysis accuracy by 25\%.
    \item Advanced expertise in quantum gates and optimization algorithms applied to machine learning.
\end{itemize}
\vspace{5pt}
\textbf{Abdus Salam International Centre for Theoretical Physics} \hfill Trieste, Italy

\textbf{Undergraduate Researcher} \hfill May 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Engineered \texttt{Python}-based statistical models, reducing machine learning evaluation times by 40\%.
    \item Applied Topological Data Analysis to extract insights from complex datasets.
    \item Collaborated with 4 data scientists to enhance algorithm precision by 25\% on high-dimensional data.
\end{itemize}
\vspace{5pt}
\textbf{Didi Chuxing Technology Co.} \hfill CDMX, Mexico

\textbf{Data Science Intern} \hfill Jun 2023 – Oct 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Analyzed 250K+ sales rows with \texttt{SQL}, driving strategic decisions that improved efficiency by 30\%.
    \item Developed \texttt{Python}-based data models, reducing processing time by 50\% and boosting accuracy by 25\%.
    \item Designed \texttt{PowerBI} dashboards to visualize KPIs, enabling actionable insights for LATAM operations.
    processing time of 30\%.
\end{itemize}
\vspace{5pt}
\textbf{Universidad Autónoma Metropolitana} \hfill CDMX, Mexico

\textbf{Data Science Researcher} \hfill May 2021 – Oct 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Leveraged PySpark to streamline data pipelines, improving processing efficiency by 30\%.
    \item Enhanced visualizations with parallel computing techniques, cutting computation time by 40\%.
    \item Applied HPC tools to optimize data analysis workflows, enabling large-scale simulations.
\end{itemize}
\vspace{10pt}
\begin{center}
    \textbf{Education}
\end{center}
\textbf{Universidad Autónoma Metropolitana} \hfill CDMX, Mexico

B.Sc. Physics. GPA 3.72/4.00 \hfill Oct 2023

\textbf{Universidad Nacional Autónoma de México} \hfill CDMX, Mexico

B.Sc. Mathematics. GPA 3.80/4.00 \hfill Jul 2024

\vspace{10pt}
\begin{center}
    \textbf{Projects}
\end{center}
\textbf{ISINGenerator} \hfill \href{https://github.com/erick-rios/ISINGenerator}{Github}

Open-source library facilitating advanced analysis of energy, magnetization, and topological domains in a 2D Ising Model; enhanced simulation accuracy by 50\% and received 2+ GitHub stars within 3 months

\textbf{Topological Data Analysis League MX} \hfill \href{https://github.com/erick-rios/topological_data_analysis_mx_league}{Github}

Scraped, cleaned, and visualized Mexican Soccer League data using \texttt{ETL} and Mapper Graphs.

\vspace{10pt}
\begin{center}
    \textbf{Skills}
\end{center}
\textbf{Technical:} C/C++, Java, Python, SQL, MATLAB, R, Power BI

\textbf{Language:} Spanish(Native), English(C1), Japanese(J5)

\textbf{Laboratory:} High Performance Computing (HPC) tools, Convolutional Neural Networks (CNN), Parallel computing techniques, Artificial Intelligence development.

\textbf{Softskills:} Teamwork, Problem-solving, Communication, Leadership, Time Management.
\end{document}
