\documentclass[6pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[left=1.06cm,top=0.98cm,right=1.06cm,bottom=0.49cm]{geometry}

\begin{document}
\begin{center}
    \textbf{ERICK JESUS RIOS GONZALEZ}\\ 
    \hrulefill
\end{center}

\begin{center}
    Coyoac\'an \textbullet \ CDMX, 04300 \textbullet \ erickjesusriosgonzalez@gmail.com \textbullet \  951 587 1972
\end{center}

\vspace{0.5pt}

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Faculty of Sciences, UNAM} \hfill CDMX, Mexico

\textbf{Teaching Assistant} \hfill Aug 2024 - Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Automated grade analysis using \texttt{Python}, reducing administrative workload by 30\%.
    \item Developed dashboards in \texttt{PowerBI} to monitor student performance, enabling data-driven interventions.
    \item Conducted exploratory data analysis (EDA) to optimize academic support strategies.
\end{itemize}
\vspace{5pt}
\textbf{International Centre for Theoretical Physics (ICTP)} \hfill Trieste, Italy

\textbf{Research Intern} \hfill May 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Studied advanced techniques for machine learning in high-dimensional statistics.
    \item Developed and implemented statistical models for complex data analysis.
    \item Collaborated with an international team to enhance algorithmic efficiency in predictive tasks.
\end{itemize}
\vspace{5pt}
\textbf{South America Institute for Fundamental Research (ICTP-SAIFR)} \hfill São Paulo, Brazil

\textbf{Research Intern} \hfill Oct 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Participated in a Quantum Machine Learning project, implementing quantum algorithms with Qiskit.
    \item Enhanced data clustering techniques, improving efficiency by 40\%.
    \item Designed quantum computing models for machine learning applications, increasing accuracy by 25\%.
\end{itemize}
\vspace{5pt}
\textbf{Didi Chuxing Technology Co.} \hfill CDMX, Mexico

\textbf{Data Science Intern} \hfill Jun 2023 -- Oct 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Analyzed 250K+ sales rows with \texttt{SQL}, driving strategic decisions that improved efficiency by 30\%.
    \item Built \texttt{Python}-based machine learning models, reducing processing time by 50\% and boosting accuracy by 25\%.
    \item Designed \texttt{PowerBI} dashboards to visualize KPIs, enabling actionable insights for LATAM operations.
\end{itemize}
\vspace{5pt}
\textbf{Universidad Aut\'onoma Metropolitana} \hfill CDMX, Mexico

\textbf{Data Science Researcher} \hfill May 2021 -- Oct 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Applied \texttt{PySpark} to streamline data pipelines, improving processing efficiency by 30\%.
    \item Enhanced data visualization techniques using \texttt{Matplotlib} and \texttt{Seaborn}.
    \item Built statistical models for large-scale simulations, leveraging HPC tools for parallel computing.
\end{itemize}
\vspace{10pt}
\begin{center}
    \textbf{Education}
\end{center}

\textbf{Universidad Aut\'onoma Metropolitana} \hfill CDMX, Mexico

B.Sc. Physics. GPA: 3.72/4.00 \hfill Oct 2023

\textbf{Universidad Nacional Aut\'onoma de M\'exico} \hfill CDMX, Mexico

B.Sc. Mathematics. GPA: 3.80/4.00 \hfill Jul 2024

\vspace{10pt}
\begin{center}
    \textbf{Projects}
\end{center}
\textbf{ISINGenerator} \hfill \href{https://github.com/erick-rios/ISINGenerator}{Github}

Open-source library facilitating advanced analysis of energy, magnetization, and topological domains in a 2D Ising Model; enhanced simulation accuracy by 50\%.

\textbf{Topological Data Analysis League MX} \hfill \href{https://github.com/erick-rios/topological_data_analysis_mx_league}{Github}

Scraped, cleaned, and visualized Mexican Soccer League data using \texttt{ETL} and Mapper Graphs.

\vspace{10pt}
\begin{center}
    \textbf{Skills}
\end{center}
\textbf{Technical:} Python, SQL, PySpark, TensorFlow, Scikit-Learn, Tableau, Matplotlib, Seaborn

\textbf{Languages:} Spanish (Native), English (C1)

\textbf{Soft Skills:} Teamwork, Problem-solving, Attention to Detail, Communication

\textbf{Tools:} Power BI, Git, JIRA, Microsoft Office (Excel, Word, PowerPoint)
\end{document}

